Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-02 supp.rnw
Add "S" to figure numbers in the supplementary.
Add axis labels to the supplementary plots of model fit.

\begin{document}
\maketitle

%TODO: x and y axis labels.
<<echo=FALSE>>=
	model_fit_plot <- function(parameters) {
		plot_df <- data.frame(
			observed = input_data$response_vector,
			fitted = input_data$get_fitted_values(parameters),
			focal = species_dat$name[input_data$focal_vector]
		)
		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal)
		return(plot)
	}

@@

%TODO: Reorder partial residual/model fit plots to use same species order as other figures.
%TODO: Add "S" to figure numbers.
\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(best_parameters))
	@

>>>>

\begin{document}
\beginsupplementary
\maketitle

%TODO: x and y axis labels.
<<echo=FALSE>>=
	model_fit_plot <- function(parameters) {
		plot_df <- data.frame(
			observed = input_data$response_vector,
			fitted = input_data$get_fitted_values(parameters),
			focal = species_dat$name[input_data$focal_vector]
		)
		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal) +
			labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
		return(plot)
	}

@@

%TODO: Reorder partial residual/model fit plots to use same species order as other figures.
\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(best_parameters))
	@
